On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-04-18 Manuscript/manuscript.tex
Error Fix

\jy{Make it flow better and conciser}
The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, CI}$ and $\hat\theta_{U, CI}$ be the lower bound and upper bound,
respectively, $ for $CI \in \{1, \ldots, n_{CI}\}$, where $n_{CI} is the number of 
CIs.
Then $cov = \#\{$\hat\theta_{L, CI}$ < \theta < $\hat\theta_{U, CI}$ \}/n_{CI}$, $ 
for $CI \in \{1, \ldots, n_{CI}\}$.
The coverage rate is, of course, a
point estimate of a proportion, so a 95\% CI of this coverage
proportion (with $n_{CI} = 10000$) can be constructed. If the proportion
.95 is included in the interval, the block bootstrap method is likely
performing
well. If all values in the interval are below .95, the results suggest that the
method either is providing an inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

>>>>

\jy{Make it flow better and conciser}
The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, CI}$ and $\hat\theta_{U, CI}$ be the lower bound and upper bound,
respectively,  for $CI \in \{1, \ldots, n_{CI}\}$, where $n_{CI}$ is the number of 
CIs.
Then $cov = \#\{\hat\theta_{L, CI} < \theta < \hat\theta_{U, CI} \}/n_{CI}$,  
for $CI \in \{1, \ldots, n_{CI}\}$.
The coverage rate is, of course, a
point estimate of a proportion, so a 95\% CI of this coverage
proportion (with $n_{CI} = 10000$) can be constructed. If the proportion
.95 is included in the interval, the block bootstrap method is likely
performing
well. If all values in the interval are below .95, the results suggest that the
method either is providing an inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.
